---
title: "Week 10 Task Set"
author: "Destinee Ramos"
format: html
execute:
  echo: true
  warning: true
  message: true
---

#### Q1: Load and Inspect Data ------------------------------------

```{r}
## Load the saved dataset
experiment_data <- readRDS("../data/raw/experiment_data.rds")

## Take a quick look at the first few rows
head(experiment_data)

## Check the structure of the dataset
str(experiment_data)
 
```

#### Q2: Functions ------------------------------------------------

```{r}
## Generate one or more random numbers between min and max (defaults: one number between 1–10)
getRandomNumber <- function(min = 1, max = 10, number = 1) {
  sample(min:max, number)
}
 
```


```{r}
## Classify reaction times into "Fast", "Slow", or "Unknown" (default threshold = 500ms)

classify_rt <- function(rt, threshold = 500) {
  if (!is.numeric(threshold) || length(threshold) != 1) {
    stop("Error: 'threshold' must be a single numeric value.")
  }
  if (!is.numeric(rt)) {
    stop("Error: 'rt' must be numeric.")
  }
  category <- ifelse(
  is.na(rt), "Unknown",  
  ifelse(rt < threshold, "Fast", "Slow")
 )
   return(category)
}
 
##Testing the function 
function_test <- c(100,200,300,500)
classify_rt(function_test)
classify_rt(experiment_data$rt)

```
#### Q3: Loops vs Vectorization ------------------------------------------------

```{r}
##Q3.1 New Columns
experiment_data$age <- NA

##Q3.2 Loop Version
for (i in 1:nrow(experiment_data)) {
  experiment_data$age[i] <- getRandomNumber(18, 65, 1)
}

head(experiment_data)
```


```{r}
#Q3.3 Vectorized Version
experiment_data$age <- sample(18:65, nrow(experiment_data), replace = TRUE)
head(experiment_data)
```

###Q4: Control Structures on Data Frames ---------------------------

```{r}
##Q4.1 Loop

experiment_data$rt_category_loop <- NA 
for(i in 1:nrow(experiment_data)) {
    experiment_data$rt_category_loop[i] <- classify_rt(experiment_data$rt[i])
}
head(experiment_data)

```

```{r}
##Q4.2 Vectorized Version
experiment_data$rt_category_vec <- NA
experiment_data$rt_category_vec <- classify_rt(experiment_data$rt)
head(experiment_data)

```

```{r}

table(loop = experiment_data$rt_category_loop,
      vec  = experiment_data$rt_category_vec,
      useNA = "ifany")

```

#### Q5: Debugging Functions -----------------------------

```{r}
## Create Buggy Function

#flag_fast <- function(rt_vector, threshold = 500) {
#  rt_vector < threshold
#}

#flag_fast(experiment_data$rt)

#rm(threshold)

#flag_fast(experiment_data$rt)

```

#### Q6: Debugging Tools in Action -----------------------------

```{r}
##Q6.1 Reproduce the Issue

subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))

```

```{r}
##Q6.2 Investigate Missingness

# How many NAs overall?
sum(is.na(experiment_data$rt))

# How many NAs by condition?
tapply(is.na(experiment_data$rt), experiment_data$condition, sum)

# Optional: quick sanity checks
summary(experiment_data$rt)
with(experiment_data, table(condition, is.na(rt)))

```

```{r}
##Q6.3 Fix the Calculation

subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean, na.rm = TRUE)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))

print(subject_means)

```

#### Q7: Using AI for Debugging or Refactoring -----------------------

```{r}

iat_data <- data.frame(
  participant = 1:5,
  affiliation = c("dem", "rep", "dem", "rep", "dem"),
  rt = c(220, 350, 430, 440, 225)
)

##mean(iat_data$condition)

str(iat_data)
aggregate(rt ~ affiliation, data = iat_data, FUN = mean)


```

Q7.2 AI Prompt

Using Chat to debug was both good and bad. It did point out and digest the entire error message, which was very helpful. It also walked me through a few different solutions I could try based on what I actually wanted to accomplish with this code. I wish that it had included how to check using the str() function, like what was suggested in the class notes (so I verified this myself). AI gives you the code you can use to fix the error, however, they don't really help you understand the solutions step by step. I inputted the fixed code into R and it did work, however, it didn't really tell me why this code worked. Using " ~ " and  FUN = mean where completely new to me and it didn't explain what these were doing, it just fixed the issue and worked.


#### Q8: Saving and Reloading Objects -----------------------------

```{r}

##Q8.1 Cleaned Dataset

write.csv(experiment_data, "../data/cleaned/experiment_data.csv", row.names = FALSE)
saveRDS(experiment_data, "../data/cleaned/experiment_data.rds")
list.files("../data/cleaned")

##Q8.2 Multiple Objects

## Save multiple objects together
save(experiment_data, subject_means, file = "../data/cleaned/objects.RData")

## Clear the environment
rm(list = ls())

## Reload them later
load("../data/cleaned/objects.RData")

```


