---
title: "AI Refactor Project 2 "
author: "Destinee Ramos"
format:
  html:
    fig-number: true
execute:
  echo: true
  warning: true
  message: true
---

Summary of re factoring choices
+ Most of my re factoring included getting rid of for loops and replacing them with vectorized code. Getting rid of a for loop in both summarize_behavior and build_participant_wide allowed me to better optimize my code and make it as short and practical as possible. In R, code will automatically loop through rows, therefore, so that others can best read and reproduce my code, I decided to get rid of for loops. Vectorized versions are much shorter and simpler (in my opinion). My third place where I re factored code was in summarize_behavior when I got rid of matrices in the code, and instead, used subset to index by name (instead of position). I did this because when working with large data sets and passing them between peers and colleague, indexing by position can be dangerous, as if one thing gets put out of place, it is easy to move forward analyzing the completely wrong variable Therefore, indexing my name instead makes the code easier to read (you know exactly what variable you're referring to) and safer to use as large data sets are modified and passed along.  

Re factoring #1 in build_participant_wide (for loop into vectorized version)
```{r}
##OLD CODE 
if (FALSE) {
  rows <- list()
  for (i in seq_along(files)) {
   file_name <- files[i]
   rows[[i]] <- import_and_process(file_name)
  }
}

##NEW CODE 
if (FALSE) {
    rows <- lapply(files, import_and_process)
}

```
 
Re factoring #2 in summarize_behavior (for loop into vectorized version)
```{r}

##OLD CODE 
if (FALSE) {
  valid_data_rt$rt_centered <- NA_real_
  for (i in 1:nrow(valid_data_rt)) {
  valid_data_rt$rt_centered[i] <- valid_data_rt$rt[i] - mean(valid_data_rt$rt, na.rm = TRUE)
  }
}

##NEW CODE
if (FALSE) {
  valid_data_rt$rt_centered <- valid_data_rt$rt - mean(valid_data_rt$rt, na.rm = TRUE)
}

```
 
 
 Re factoring #3 in summarize_behvaior (index by name, instead of position) 
```{r}
## OLD CODE 
if (FALSE) {
  valid_data_rt <- data[data[ , 3] >= 300 & data[ , 3] <= 900 & data[ , 12] == TRUE, ]
  valid_data_acc <- data[data[ , 3] >= 300 & data[ , 3] <= 900, ]
}

##NEW CODE 
if (FALSE) {
  valid_data_rt <- subset(data, rt >= 300 & rt <= 900 & correct == TRUE)
  valid_data_acc <- subset(data, rt >= 300 & rt <= 900)
}

```


AI Optimization   


Ideas AI gave for unedited project 
+ 
+ 
+ 


Ideas AI gave for refactored version 
+ 
+ 
+ 

Comparison section: 

Then write a comparison section: Discuss where your own changes matched the AI’s ideas, where you differed, and what you learned from the comparison. This can include organizational changes, naming conventions, function design, file structure, avoidance of repeated code, or any other structural points the AI highlighted.

Optional but encouraged: examples You may include small code snippets that show “before vs. after” improvements, as long as you keep them short and focused.



